intro

### 2022-01-28 06_Paper/ER-ED/TheoreticalBackground.Rmd
Update TheoreticalBackground.Rmd

The postulation of *adaptive* and *maladaptive* strategies was put in a new perspective with the concept of ER flexibility.
Similar to other psychological domains, e.g., attention and goal pursuit, *maladaptive* now refers to inflexible strategy use or use of strategies that are hindering in the achievement of goals [@Aldao2015].
First, adaptive flexible ER requires having a large repertoire of ER strategies [@Aldao2015]. 
For example, greater ER variability is related to reduced negative affect and therefore beneficial in daily life [@Blanke2020].
Second, strategies have to be chosen from the repertoire that are useful for goal achieving.
This selection of strategies is influenced by numerous factors.
For example, it was shown that the intensity of a stimulus or situation plays a role in the choice [@Sheppes2011]. 
Higher intensity of the stimulus leads to a choice of rather disengaging strategies, like distraction [@Sheppes2011;@Sheppes2014].
Further influencing factors are for example extrinsic motivation (e.g. monetary incentives), motivational determinants (i.e. hedonic regulatory goals), and effort [@Sheppes2014;@Scheffel2021].
Especially for effort, Scheffel and colleagues [-@Scheffel2021] could show that the choice for an ER strategy is mainly influenced by effort.
### Willst du hier nicht lieber "in our previous work" oder sowas schreiben? Wenn die Autoren von sich selbst in der dritten Person sprechen, hab ich immer das Gefühl, dass sie die Lesenden in die Irre führen wollen, indem sie etwas referenzieren, was eigentlich von ihnen selbst ist.
In this study, participants used the strategies distancing and suppression while inspecting emotional pictures.
Afterwards they could choose, which strategy they want to use again.
Participants tended to re-apply the strategy that was less effortful, even though it was not the most effective one - in this case: Suppression.
Interestingly, the choice was independent of self reported habitual use of suppression and reappraisal.

>>>>

The postulation of *adaptive* and *maladaptive* strategies was put in a new perspective with the concept of ER flexibility.
Similar to other psychological domains, e.g., attention and goal pursuit, *maladaptive* now refers to inflexible strategy use or use of strategies that are hindering in the achievement of goals [@Aldao2015].
First, adaptive flexible ER requires having a large repertoire of ER strategies [@Aldao2015]. 
For example, greater ER variability is related to reduced negative affect and therefore beneficial in daily life [@Blanke2020].
Second, strategies have to be chosen from the repertoire that are useful for goal achieving.
This selection of strategies is influenced by numerous factors.
For example, it was shown that the intensity of a stimulus or situation plays a role in the choice [@Sheppes2011]. 
Higher intensity of the stimulus leads to a choice of rather disengaging strategies, like distraction [@Sheppes2011;@Sheppes2014].
Further influencing factors are for example extrinsic motivation (e.g. monetary incentives), motivational determinants (i.e. hedonic regulatory goals), and effort [@Sheppes2014;@Scheffel2021].
Especially for effort, in our previous work we could show that the choice for an ER strategy is mainly influenced by effort [@Scheffel2021].

In this study, participants used the strategies distancing and suppression while inspecting emotional pictures.
Afterwards they could choose, which strategy they want to use again.
Participants tended to re-apply the strategy that was less effortful, even though it was not the most effective one - in this case: Suppression.
Interestingly, the choice was independent of self reported habitual use of suppression and reappraisal.
